Discrep_Patterns

### 2024-11-04 misc/discrep.qmd
add proportion tables and SE

### Study 1

@@

@@

@@

bind_rows(
  s1_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      dataset = "Before exclusions"
    ),
  s1_agg4 |> 
    filter(!(id %in% s1_discrep_ids)) |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      dataset = "After exclusions"
    )
) |>
  pivot_wider(
    names_from = dataset,
    values_from = c(mean, sd, n),
    names_glue = "{dataset}_{.value}"
  ) |>
  gt() |>
  tab_header(
    title = "Study 1: Performance Before and After Exclusions"
  ) |>
  fmt_number(
    columns = contains("mean"),
    decimals = 2
  ) |>
  fmt_number(
    columns = contains("sd"),
    decimals = 2
  ) |>
  cols_label(
    refClass = "Reference Class",
    `Before exclusions_mean` = "Mean",
    `Before exclusions_sd` = "SD",
    `Before exclusions_n` = "N",
    `After exclusions_mean` = "Mean",
    `After exclusions_sd` = "SD",
    `After exclusions_n` = "N"
  ) |>
  tab_spanner(
    label = "Before Exclusions",
    columns = starts_with("Before")
  ) |>
  tab_spanner(
    label = "After Exclusions",
    columns = starts_with("After")
  )

@@

bind_rows(
  s2_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      dataset = "Before exclusions"
    ),
  s2_agg4 |> 
    filter(!(id %in% s2_discrep_ids)) |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      dataset = "After exclusions"
    )) |> 
    pivot_wider(names_from = dataset,
    values_from = c(mean, sd, n),
    names_glue = "{dataset}_{.value}") |> gt() |>
    tab_header(title = "Study 2: Performance Before and After Exclusions") |>
    cols_label(
    refClass = "Reference Class",
    `Before exclusions_mean` = "Mean",
    `Before exclusions_sd` = "SD",
    `Before exclusions_n` = "N",
    `After exclusions_mean` = "Mean",
    `After exclusions_sd` = "SD",
    `After exclusions_n` = "N"
  ) |>
  tab_spanner(
    label = "Before Exclusions",
    columns = starts_with("Before")
  ) |>
  tab_spanner(
    label = "After Exclusions",
    columns = starts_with("After"))

@@

>>>>

### Study 1 - Subject counts

@@

prop.table(xtabs(~refClass,s1)) |> kable()
prop.table(xtabs(~refClass+calc,s1)) |> kable()
prop.table(xtabs(~refClass+state,s1)) |> kable()

### Study 2 - Subject counts 
```{r}

@@

prop.table(xtabs(~refClass,s2_long)) |> kable()
prop.table(xtabs(~refClass+state,s2_long))
prop.table(xtabs(~refClass+calc,
s2_long |> mutate(calc=case_when(calc=="Calculator" ~ "Used Calculator",
                      calc=="No Calculator" ~ "No Calculator")))) |> kable()
```

##  Performance before and after exclusions

@@

bind_rows(
  s1_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd(pct)/sqrt(n),
      dataset = "Before exclusions"
    ),
  s1_agg4 |> 
    filter(!(id %in% s1_discrep_ids)) |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd(pct)/sqrt(n),
      dataset = "After exclusions"
    )
) |>
  pivot_wider(
    names_from = dataset,
    values_from = c(mean, sd, se,n),
    names_glue = "{dataset}_{.value}"
  ) |>
  gt() |>
  tab_header(
    title = "Study 1: Performance Before and After Exclusions"
  ) |>
  fmt_number(
    columns = contains("mean"),
    decimals = 2
  ) |>
  fmt_number(
    columns = contains("sd"),
    decimals = 2
  ) |>
  cols_label(
    refClass = "Reference Class",
    `Before exclusions_mean` = "Mean",
    `Before exclusions_sd` = "SD",
    `Before exclusions_se` = "SE",
    `Before exclusions_n` = "N",
    `After exclusions_mean` = "Mean",
    `After exclusions_sd` = "SD",
    `After exclusions_se` = "SE",
    `After exclusions_n` = "N"
  ) |>
  tab_spanner(
    label = "Before Exclusions",
    columns = starts_with("Before")
  ) |>
  tab_spanner(
    label = "After Exclusions",
    columns = starts_with("After")
  )

@@

bind_rows(
  s2_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd(pct)/sqrt(n),
      dataset = "Before exclusions"
    ),
  s2_agg4 |> 
    filter(!(id %in% s2_discrep_ids)) |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd(pct)/sqrt(n),
      dataset = "After exclusions"
    )) |> 
    pivot_wider(names_from = dataset,
    values_from = c(mean, sd,se, n),
    names_glue = "{dataset}_{.value}") |> gt() |>
    tab_header(title = "Study 2: Performance Before and After Exclusions") |>
    cols_label(
    refClass = "Reference Class",
    `Before exclusions_mean` = "Mean",
    `Before exclusions_sd` = "SD",
    `Before exclusions_se` = "SE",
    `Before exclusions_n` = "N",
    `After exclusions_mean` = "Mean",
    `After exclusions_sd` = "SD",
    `After exclusions_se` = "SE",
    `After exclusions_n` = "N"
  ) |>
  tab_spanner(
    label = "Before Exclusions",
    columns = starts_with("Before")
  ) |>
  tab_spanner(
    label = "After Exclusions",
    columns = starts_with("After"))

@@

s1_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd(pct)/sqrt(n),
      dataset = "Before exclusions"
    )

s1_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se=sd/sqrt(n),
      dataset = "Before exclusions"
    )

s1_agg4 |> 
    group_by(refClass) |> 
    summarise(
      mean = mean(pct),
      sd = sd(pct),
      n = n(),
      se = sd/sqrt(n),  # Using sd calculated above
      dataset = "After exclusions"
    )
